%
% This is an example of a vita page.  
% Format is not tightly specified. This example comes from Lili Ma.
%
%  Time-stamp: "[vita.tex] last modified by Scott Budge (scott) on 2012-07-16 (Monday, 16 July 2012) at 11:18:06 on goga"
%
%  Info: $Id$   USU
%  Revision: $Rev$
% $LastChangedDate$
% $LastChangedBy$
%

\begin{vita}

\begin{center}
{\Large \bf John Q. Engineer}\\
\end{center}

\section*{Published Journal Articles}
    \begin{itemize}
    \item Rational Radial Distortion Models of Camera Lenses with Analytical Solution for Distortion Correction, Lili
    Ma, YangQuan Chen, and Kevin L. Moore, {\it International Journal of Information Acquisition}, {\it Accepted}.

    \item A Small Mobile Robot for Security and Inspection Operations, N.S. Flann, K. L. Moore, and Lili Ma, {\it Control Engineering Practice}, vol. 10, pp. 1265-1270,
    2002.
    \end{itemize}

\section*{Published Conference Papers}
    \begin{itemize}
    \item Range Identification for Perspective Dynamic Systems Using
      Linear Approximation, Lili Ma, YangQuan Chen, and Kevin
      L. Moore, in {\it Proc. IEEE Int. Conf. on Robotics and
        Automation (ICRA)},
    2004.
  \item Range Identification for Perspective Dynamic System with
    Single Homogeneous Observation, Lili Ma, YangQuan Chen, and Kevin
    L. Moore, in {\it Proc. IEEE Int. Conf. on Robotics and Automation (ICRA)},
    2004.
  \item Blind Detection and Compensation of Camera Lens Geometrical
    Distortions, Lili Ma and YangQuan Chen, {\it SIAM Imaging
      Science}, 2004.
  \item Flexible Camera Calibration Using a New Analytical Radial
    Undistortion Formula with Application to Mobile Robot
    Localization, Lili Ma, YangQuan Chen, and Kevin L. Moore, in {\it
      Proc. Int. Symposium on Intelligent Control (ISIC)}, 2003.
  \item Sonar and Laser Based HIMM Map Building for Collision
    Avoidance for Mobile Robots, Lili Ma and Kevin L. Moore, in {\it
      Proc. International Symposium on Intelligent Control (ISIC)},
    2003.
  \item Wireless Visual Servoing for ODIS - An Under Car Inspection
    Mobile Robot, Lili Ma, Matthew Berkemeier, YangQuan Chen, Morgan
    Davidson, Vikas Bahl, and Kevin L. Moore, in {\it Proc. IFAC World
      Congress}, Spain, July, 2002.
  \item Visual Servoing of an Omni-Directional Mobile Robot for
    Alignment with Parking Lot Lines, Matthew Berkemeier, Morgan
    Davidson, Vikas Bahl, YangQuan Chen, and Lili Ma, in {\it Proc.
      IEEE Int.  Conf. on Robotics and Automation (ICRA)}, May 2002.
  \item Some Sensing and Perception Techniques for an Omnidirectional
    Ground Vehicle with a Laser Scanner, Zhen Song, YangQuan Chen,
    Lili Ma, and You Chung Chung, in {\it Proc. IEEE Int. Symposium on
      Intelligent Control (ISIC)}, October 2002.
  \item A Small Mobile Robot For Security and Inspection Operations,
    Flann NS, Moore KL, and Ma L, in {\it Proc. IFAC Conference on Telematics
      Applications in Automation and Robotics}, July 2001.
    \end{itemize}

\end{vita}
